---
title: "BC outbreak data fitting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BC outbreak data fitting}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev="png", collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
options(mc.cores = parallel::detectCores())

# load libraries
library(tidyverse)
library(rstan)
library(kableExtra)
library(here)
library(tidybayes)
library(latex2exp)
library(cr0eso)


# constants
bootstrap_options <- c("striped", "hover")

```

## Load long-term healthcare outbreak data

Data loaded includes number of cases since outbreak on a given day for each location, the number of outbreaks, the size of the facility, as well as the labels for the outbreaks.

```{r load data}



n_outbreaks <- length(BC_LTHC_outbreaks_100Imputs[[1]]$capacity)
outbreak_sizes <- BC_LTHC_outbreaks_100Imputs[[1]]$capacity
outbreak_cases_series <- BC_LTHC_outbreaks_100Imputs[[1]]$time_series
ob_codes <- BC_LTHC_outbreaks_100Imputs[[1]]$Location
tmax <- 50

# create matrix for cases
# outbreak_cases <- matrix(nrow=tmax,ncol=n_outbreaks)
# 
# for(i in 1:length(outbreak_cases_series)){
#   # case number for outbreak i
#   ob_cases <- outbreak_cases_series[[i]]
#   # truncate at 50
#   ob_cases <- ob_cases[1:min(tmax,length(ob_cases))]
#   padded_ob_cases <- replace(rep(0,tmax), seq(from= 1, to = length(ob_cases)), 
#                              ob_cases)
#   outbreak_cases[,i] <- padded_ob_cases
# }

outbreak_cases <- BC_LTHC_outbreaks_100Imputs[[1]]$case_matrix

# plot cases from matrix
as_tibble(outbreak_cases,rownames="time") %>%
  mutate(time = as.double(time)) %>%
  pivot_longer(-time,names_to = "location",values_to="cases") %>%
  ggplot(aes(x=time,y=cases,color=location)) +
  geom_line() +
  theme(legend.position = "none")
  


```

## Fit model

Fit model including estimating intervention. This code chunk is not run in the
vignette, but provides the syntax for how to produce posterior samples. The
`bc_fit` data object is including in the package.

```{r fit model, eval = FALSE}
bc_fit <- seir_model_fit(tmax,n_outbreaks,outbreak_cases,outbreak_sizes,
                       intervention_switch = TRUE,
                       multilevel_intervention = FALSE)

```



## Model diagnositc checking

```{r model diagnostic plot}
pairs(bc_fit$model, pars = c("params"))
rstan::check_hmc_diagnostics(bc_fit$model)
# print(mod)

traceplot(bc_fit$model, pars = c("params[1]", "params[2]"), inc_warmup = TRUE, nrow = 2)

rhats <- bayesplot::rhat(bc_fit$model)
rhats[rhats>1.03]
bayesplot::mcmc_rhat(rhats)

bayesplot::mcmc_nuts_divergence(bayesplot::nuts_params(bc_fit$model), 
                                bayesplot::log_posterior(bc_fit$model))

```


## Plot model output

```{r}
# Extract the posterior samples to a structured list:
posts <- rstan::extract(bc_fit$model)

extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and zeta
result <- hom_plot_r0_by_location(extracted_posts=extracted_posts)

# plot results
show(result$plot + labs(y=TeX("$R_{0,k}$")))

result$table %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling(bootstrap_options=bootstrap_options)

```

## Plot model fit to incidence

```{r, fig.height=12,fig.width=8}
extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and r0
result <- hom_plot_incidence_by_location(extracted_posts=extracted_posts,
                                         outbreak_cases = outbreak_cases)
# plot results
result$plot


```

## Plot counterfactual scenario

The code below extracts and plots the counterfactual scenario and also provides a summary table of cases by location in the baseline, scenario, where there was no intervention and the difference and proportional difference representing the cases averted. The final row provides a total summary of cases.

```{r, fig.height=12,fig.width=8}
result <- hom_plot_counterfactual_by_location(bc_fit,
                                      outbreak_cases = outbreak_cases)

# plot results
show(result$plot)



# show table of results
result$table %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = c("striped","responsive"))

```

## Fit hierarcichal intervention model

Fit model including estimating intervention by each location in a hierarchical
design,

```{r fit zeta model, eval = FALSE}
bc_fit_zeta <- seir_model_fit(tmax,n_outbreaks,outbreak_cases,outbreak_sizes,
                       intervention_switch = TRUE,
                       multilevel_intervention = TRUE)



```



## Plot model output - zeta model

```{r}
# Extract the posterior samples to a structured list:
posts <- rstan::extract(bc_fit_zeta$model)

extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and zeta
result <- hom_plot_r0_by_location(extracted_posts=extracted_posts)

# plot results
show(result$plot + labs(y=TeX("$R_{0,k}$")))

result$table %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling(bootstrap_options=bootstrap_options)


```


## Plot hierarchical intervention strength by location (zeta)

```{r fig.hieght=12,fig.width=8}

result <- hom_plot_zeta_by_location(extracted_posts=extracted_posts)

# plot results
show(result$plot)

result$table %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling(bootstrap_options=bootstrap_options)


```

## Plot model fit to incidence - zeta model

```{r, fig.height=12,fig.width=8}
extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and r0
result <- hom_plot_incidence_by_location(extracted_posts=extracted_posts,
                                         outbreak_cases = outbreak_cases)
# plot results
result$plot


```



## Plot counterfactual scenario - zeta model

The code below extracts and plots the counterfactual scenario and also provides a summary table of cases by location in the baseline, scenario, where there was no intervention and the difference and proportional difference representing the cases averted. The final row provides a total summary of cases.

```{r, fig.height=12,fig.width=8}
result <- hom_plot_counterfactual_by_location(bc_fit_zeta,
                                      outbreak_cases = outbreak_cases)

# plot results
show(result$plot)

# show table of results
result$table %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = c("striped","responsive"))

```

## Create parameter comparison table


```{r parameter comparison table}

res <- create_pub_tables("Fixed intervention"= bc_fit,
                               "Multiple intervention" = bc_fit_zeta)

res %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped")

```
