---
title: "BC outbreak data fitting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BC outbreak data fitting}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev="png", collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
options(mc.cores = parallel::detectCores())

# load libraries
library(tidyverse)
library(rstan)
library(kableExtra)
library(here)
library(tidybayes)
library(latex2exp)
library(cr0eso)
library(scales)
library(ggsidekick)


# constants
bootstrap_options <- c("striped", "hover")

```

## Load long-term healthcare outbreak data

Data loaded includes number of cases since outbreak on a given day for each location, the number of outbreaks, the size of the facility, as well as the labels for the outbreaks.

```{r load data}



n_outbreaks <- length(BC_LTHC_outbreaks_100Imputs[[100]]$capacity)
outbreak_sizes <- BC_LTHC_outbreaks_100Imputs[[100]]$capacity
outbreak_cases_series <- BC_LTHC_outbreaks_100Imputs[[100]]$time_series
ob_codes <- BC_LTHC_outbreaks_100Imputs[[100]]$Location


outbreak_cases <- BC_LTHC_outbreaks_100Imputs[[100]]$case_matrix

tmax <- 50

# plot cases from matrix
as_tibble(outbreak_cases,rownames="time") %>%
  mutate(time = as.double(time)) %>%
  pivot_longer(-time,names_to = "location",values_to="cases") %>%
  ggplot(aes(x=time,y=cases,color=location)) +
  geom_line() +
  theme(legend.position = "none")
  


```

## Fit model

Fit model including estimating intervention. This code chunk is not run in the
vignette, but provides the syntax for how to produce posterior samples. The
`bc_fit` data object is including in the package.

```{r fit model, eval = FALSE}
stan_mod <- rstan::stan_model(system.file("stan", "hierarchical_SEIR_incidence_model.stan", package = "cr0eso"))

bc_fit <- seir_model_fit(
                       stan_model = stan_mod,
                       tmax,n_outbreaks,outbreak_cases,outbreak_sizes,
                       intervention_switch = TRUE,
                       multilevel_intervention = FALSE,
                       iter = 2000)

```



## Model diagnostic checking

```{r model diagnostic plot}
pairs(bc_fit$model, pars = c("params"))
rstan::check_hmc_diagnostics(bc_fit$model)
# print(mod)

traceplot(bc_fit$model, pars = c("params[1]", "params[2]"), inc_warmup = TRUE, nrow = 2)

rhats <- bayesplot::rhat(bc_fit$model)
rhats[rhats>1.03]
bayesplot::mcmc_rhat(rhats)

bayesplot::mcmc_nuts_divergence(bayesplot::nuts_params(bc_fit$model), 
                                bayesplot::log_posterior(bc_fit$model))

```

## Re-label facilities

Extract the posterior sample and re-label the facilities by their estimated mean $R_0^k$,

```{r}
# Extract the posterior samples to a structured list:
posts <- rstan::extract(bc_fit$model)



location_labels <- spread_draws(bc_fit$model,r0k[location]) %>% 
  mutate(location = as.character(location)) %>%
  group_by(location) %>% 
  summarise(r0 = mean(r0k)) %>% 
  arrange(r0) %>% 
  mutate(site = LETTERS[1:n()]) %>%
  select(location,site)

# get object of incidence and zeta
extracted_posts <- hom_extract_posterior_draws(posts,
                                               location_labels = location_labels) 


```

## Plot model output

```{r}

result <- hom_plot_r0_by_location(extracted_posts=extracted_posts)

# plot results
show(result$plot + labs(y=TeX("$R_{0,k}$")))

result$table %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling(bootstrap_options=bootstrap_options)

```

## Plot model fit to incidence

```{r, fig.height=12,fig.width=8}

result <- hom_plot_incidence_by_location(extracted_posts=extracted_posts,
                                         outbreak_cases = outbreak_cases,
                                         location_labels = location_labels)
# plot results
result$plot


```

## Plot counterfactual scenario

The code below extracts and plots the counterfactual scenario and also provides a summary table of cases by location in the baseline, scenario, where there was no intervention and the difference and proportional difference representing the cases averted. The final row provides a total summary of cases.

```{r, fig.height=12,fig.width=8}
result <- hom_plot_counterfactual_by_location(bc_fit,
                                      outbreak_cases = outbreak_cases,
                                      location_labels = location_labels)

# plot results
show(result$plot)



# show table of results
result$table %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = c("striped","responsive"))

```

## Fit hierarcichal intervention model

Fit model including estimating intervention by each location in a hierarchical
design,

```{r fit zeta model, eval = FALSE}
bc_fit_zeta <- seir_model_fit(
  stan_model = stan_mod,
  tmax,n_outbreaks,outbreak_cases,outbreak_sizes,
  intervention_switch = TRUE,
  multilevel_intervention = TRUE,
                       iter = 2000)



```



## Plot model output - zeta model

```{r}
# Extract the posterior samples to a structured list:
posts <- rstan::extract(bc_fit_zeta$model)

extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and zeta
result <- hom_plot_r0_by_location(extracted_posts=extracted_posts)

# plot results
show(result$plot + labs(y=TeX("$R_{0,k}$")))

result$table %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling(bootstrap_options=bootstrap_options)


```


## Plot hierarchical intervention strength by location (zeta)

```{r fig.hieght=12,fig.width=8}

result <- hom_plot_zeta_by_location(extracted_posts=extracted_posts)

# plot results
show(result$plot)

result$table %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling(bootstrap_options=bootstrap_options)


```

## Plot model fit to incidence - zeta model

```{r, fig.height=12,fig.width=8}
extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and r0
result <- hom_plot_incidence_by_location(extracted_posts=extracted_posts,
                                         outbreak_cases = outbreak_cases)
# plot results
result$plot


```



## Plot counterfactual scenario - zeta model

The code below extracts and plots the counterfactual scenario and also provides a summary table of cases by location in the baseline, scenario, where there was no intervention and the difference and proportional difference representing the cases averted. The final row provides a total summary of cases.

```{r, fig.height=12,fig.width=8}
result <- hom_plot_counterfactual_by_location(bc_fit_zeta,
                                      outbreak_cases = outbreak_cases)

# plot results
show(result$plot)

# show table of results
result$table %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = c("striped","responsive"))

```

## Create parameter comparison table


```{r parameter comparison table}

res <- create_pub_tables("Fixed intervention"= bc_fit,
                               "Multiple intervention" = bc_fit_zeta)

res %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped")

```


## Plot estimates of the critical time

Using the estimates of zeta from the Bayesian hierarchichal model, we estimate the 'critical time', that is, the length of time from the introduction of outbreak interventions to R0 dropping below 1, in each facility.

```{r, fig.width = 7}
# Order rows by decreasing R0 and remove 'total'
res_order <- res[order(res$`r0 Fixed intervention`[-nrow(res)]),]
# Create critical times data frame
cr_times <- as.numeric(unlist(regmatches(res_order$`critical_time Fixed intervention`, gregexpr('?[0-9,.]+', res_order$`critical_time Fixed intervention`))))
cr_times <- as.data.frame(matrix(cr_times, ncol = 3,  byrow = TRUE))
names(cr_times)<-c("Critical_time", "Lower_CI", "Upper_CI")
cr_times <- cbind(Location = LETTERS[1:(nrow(res)-1)], cr_times) 

# Calculate attack rates
AR_table <- data.frame("Facility" = BC_LTHC_outbreaks_100Imputs[[100]]$Location,  
                  "A_r" = 100*BC_LTHC_outbreaks_100Imputs[[100]]$num_cases/BC_LTHC_outbreaks_100Imputs[[100]]$capacity)
# Order as in cr_times
AR_table <- AR_table[match(res_order$location,BC_LTHC_outbreaks_100Imputs[[100]]$Location, ),]
AR_table$Facility = LETTERS[1:(nrow(res)-1)]

cr_times$Attack_rate = AR_table$A_r

# Including uncertainty
d <- ggplot(cr_times, aes(Location, Critical_time)) +
  geom_point(aes(colour = Attack_rate/100), size=2.5, stat="identity") +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI, colour = Attack_rate/100), width = 0.6, size=0.6) +
  scale_colour_continuous(name = "Attack rate",  labels = percent, type="gradient", low=palette()[2], high=palette()[1]) +
  ylab("Critical time (days)") + #coord_cartesian(ylim=c(0,100)) + 
  theme_sleek()
d
```





