---
title: "Introduction to fitting multiple outbreak model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fitting multiple outbreak model}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(dev="png", collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
options(mc.cores = parallel::detectCores())

```

## Introduction

Load library,

```{r}
library("cr0eso")
```

## Create simulated data

The package will expect the data in a certain format, such as the following,

```{r}
# maximum time
tmax <- 21
# number of outbreaks
n_outbreaks <- 2
# number of daily cases per outbreak
outbreak_cases <- matrix(c(1,0,0,0,0,1,5,2,6,5,10,11,13,11,9,4,2,6,0,3,1,
                           1,1,0,1,0,0,0,1,3,0,3,2,0,0,3,6,5,6,6,6,10
                           ),ncol=2)
# number of susceptible individuals by location
outbreak_sizes <- c(100,100)
```


## Constructing priors

Parameterisation of the priors are kept in the list `prior_list` and can be updated shown below,

```{r}
# define list of priors
new_prior_list <- cr0eso::prior_list

# update mean of r0 prior to be 2
new_prior_list$r0_mean <- 2
```


## Fit model

Fit model with no intervention and updated priors (for speed we only fit one chain but multiple should be sampled),

```{r}

fit <- seir_model_fit(tmax,n_outbreaks,outbreak_cases,outbreak_sizes,
                       intervention_switch = FALSE,
                       priors = new_prior_list,
                       chains = 1)
```

## Plot model output

```{r}
# Extract the posterior samples to a structured list:
posts <- rstan::extract(fit$model)

extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and zeta
result <- hom_plot_r0_by_location(extracted_posts=extracted_posts)

# plot results
result$plot
```

## Plot model fit to incidence

```{r}
extracted_posts <- hom_extract_posterior_draws(posts) # get object of incidence and r0
result <- hom_plot_incidence_by_location(extracted_posts=extracted_posts,
                                         outbreak_cases = outbreak_cases)
# plot results
result$plot
```

## Plot counterfactual scenario

The code below extracts and plots the counterfactual scenario and also provides a summary table of cases by location in the baseline, scenario, where there was no intervention and the difference and proportional difference representing the cases averted. The final row provides a total summary of cases.

```{r}
result <- hom_plot_counterfactual_by_location(fit,
                                      outbreak_cases = outbreak_cases)

# plot results
show(result$plot)

# show table of results
result$table

```

## Create summary table

The code below takes the output of `seir_model_fit` and creates a table of 
$R_0$ and intervention strength $\zeta$ summaries by location as well as a total
representing the predictive distribution. Also included is a critical time column,
which is the estimated time from the outbreak to where the effective R is below
one. The function also allows for adding more than one model to compare the outputs,
for example comparing a model with intervention to one with no intervention assumed.

```{r}
create_pub_tables(model1 = fit) %>%
  knitr::kable()

```
